Context-dependent consequences of including lagged effects in demographic models

### 2022-05-23 docs/paper.Rmd
try to make a table of figures to go with lifecycle diagram
don't print/save experimental figures yet.

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
```

Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.

```{r}
#| pva,
#| fig.cap = "Population trajectories for all three IPMs in both habitats"
tar_load(c(
  ipm_det_cf,
  ipm_det_ff,
  ipm_stoch_cf,
  ipm_stoch_ff,
  ipm_dlnm_cf,
  ipm_dlnm_ff
))

>>>>

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
knitr::include_graphics(here::here("docs", "figures", "lifecycle.png"))
```

Combine above figure with this table:

| Description                                  | Deterministic    | Stochastic, kernel-resampled | Stochastic, parameter-resampled (DLNM) |
|----------------------|----------------|----------------|-------------------|
| Mature plant survival                        | $s(z)$           | $s_y(z)$                     | $s(z;\theta_{0-36})$                   |
| Seedling survival                            | $s_0$            | $s_{0_y}$                    | $s_0(\theta_{0-36})$                   |
| Mature plant growth or regression            | $G(z^\prime, z)$ | $G_y(z^\prime,z)$            | $G(z^\prime,z;\theta_{0-36})$          |
| Seedling growth into mature plant            | $G_0(z^\prime)$  | $G_{0_y}(z^\prime)$          | $G(z^\prime;\theta_{0-36})$            |
| Probability of flowering                     | $p_f(z)$         | $p_{f_y}(z)$                 | $p_f(z;\theta_{0-36})$                 |
| Size-specific fecundity                      | $f(z)$           | $f(z)$                       | $f(z)$                                 |
| Probability of germination and establishment | $g$              | $g$                          | $g$                                    |

<!--# probably can't make the figure with the table in it in R easily. -->

\
\
Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.

```{r eval=FALSE}
#| pva,
#| fig.cap = "Population trajectories for all three IPMs in both habitats"
tar_load(c(
  ipm_det_cf,
  ipm_det_ff,
  ipm_stoch_cf,
  ipm_stoch_ff,
  ipm_dlnm_cf,
  ipm_dlnm_ff
))
